### 2014-10-18 paper/abstract.tex
adding the paper in correct format

Although high performance is one of the main focus of those systems, there is less attention is paid for making high performance design for inter node communication. Most of these frameworks do not explore the parallelism making more parallel connections among nodes. Further some systems don't use efficient message serialization techniques which saves the network bandwidth. In this paper we introduce a high performance inter node communication design which explore the parallelism and serialize and parse messages efficiently to optimize the throughput.

First we compare performance between our system, Twitter storm and  Yahoo S4 using an implementation of Pan Tompkins algorithm which is used to detect QRS complexities of an ECG signal using a 2 node graph. Our results show our solution performs 4 times better than Twitter storm and 8 times 7 times better than Yahoo S4!. Then we use 4 level node graph which is used to process smart plug data to test the scalability of our system in a complex graph. Again our results shows our system linearly scales.

>>>>

Although high performance is one of the main focus of those systems, there is less attention has been paid for making high performance design for inter node communication. Most of these frameworks do not explore the parallelism making more parallel connections among nodes. Further some systems don't use efficient message serialization techniques which saves the network bandwidth. In this paper we introduce a high performance inter node communication design which explore the parallelism and serialize and parse messages efficiently to optimize the throughput.

First we compare performance between our system, Twitter storm and  Yahoo S4 using an implementation of Pan Tompkins algorithm which is used to detect QRS complexities of an ECG signal using a 2 node graph. Our results show our solution performs 4 times better than Twitter storm and 8 times better than Yahoo S4!. Then we use 4 level node graph which is used to process smart plug data to test the scalability of our system in a complex graph. Again our results shows our system linearly scales.

### 2014-10-18 paper/experiments.tex
adding the paper in correct format

\begin{figure}
        \centering
        \includegraphics[width=0.6\textwidth]{ecgGraph.png}
        \caption{ECG Process Graph}
        \label{ecgGraph}
\end{figure}
\begin{figure}
        \centering
        \includegraphics[width=0.6\textwidth]{throughput.png}
        \caption{Throughput of the systems}
        \label{throuput}
\end{figure}

@@

\begin{figure}
        \centering
        \begin{subfigure}[b]{0.45\textwidth}
                \includegraphics[width=\textwidth]{network.png}
        \end{subfigure}
        \begin{subfigure}[b]{0.45\textwidth}
                \includegraphics[width=\textwidth]{loadaverage.png}
        \end{subfigure}
        \caption{Network usage and CPU Load Average of the System}
        \label{networkandload}
\end{figure}

@@

\begin{figure}
        \centering
        \includegraphics[width=0.6\textwidth]{efficiency.png}
        \caption{Efficiency of Message serialization}
        \label{efficiency}
\end{figure}

@@

\begin{figure}
        \centering
        \includegraphics[width=0.6\textwidth]{multigraph.png}
        \caption{Multilevel Node Graph}
        \label{multigraph}
\end{figure}

@@

\begin{figure}
        \centering
        \begin{subfigure}[b]{0.45\textwidth}
                \includegraphics[width=\textwidth]{throughputs.png}
        \end{subfigure}
        \begin{subfigure}[b]{0.45\textwidth}
                \includegraphics[width=\textwidth]{networkps.png}
        \end{subfigure}
        \begin{subfigure}[b]{0.45\textwidth}
                \includegraphics[width=\textwidth]{networks.png}
        \end{subfigure}
        \begin{subfigure}[b]{0.45\textwidth}
                \includegraphics[width=\textwidth]{loadaverages.png}
        \end{subfigure}
        \caption{Scalability of the System}
        \label{scalability}
\end{figure}

>>>>

\begin{figure}[!t]
        \centering
        \includegraphics[width=3.0in]{ecgGraph.png}
        \caption{ECG Process Graph}
        \label{ecgGraph}
\end{figure}
\begin{figure}[!t]
        \centering
        \includegraphics[width=3.0in]{throughput.png}
        \caption{Throughput of the systems}
        \label{throuput}
\end{figure}

@@

\begin{figure*}[!t]
	\centering
	\subfloat[Network Usage]{\includegraphics[width=3.0in]{network.png}}
	\hfil
	\subfloat[CPU Load Average]{\includegraphics[width=3.0in]{loadaverage.png}}
	\caption{Network usage and CPU Load Average of the System}
	\label{networkandload}
\end{figure*}

@@

\begin{figure}[!t]
        \centering
        \includegraphics[width=3.0in]{efficiency.png}

        \caption{Efficiency of Message serialization}
        \label{efficiency}
\end{figure}

@@

\begin{figure}[!t]
        \centering
        \includegraphics[width=3.0in]{multigraph.png}
        \caption{Multilevel Node Graph}
        \label{multigraph}
\end{figure}

@@

%\begin{figure}
%        \centering
%        \begin{subfigure}[b]{0.45\textwidth}
%                \includegraphics[width=\textwidth]{throughputs.png}
%        \end{subfigure}
%        \begin{subfigure}[b]{0.45\textwidth}
%                \includegraphics[width=\textwidth]{networkps.png}
%        \end{subfigure}
%        \begin{subfigure}[b]{0.45\textwidth}
%                \includegraphics[width=\textwidth]{networks.png}
%        \end{subfigure}
%        \begin{subfigure}[b]{0.45\textwidth}
%                \includegraphics[width=\textwidth]{loadaverages.png}
%        \end{subfigure}
%        \caption{Scalability of the System}
%        \label{scalability}
%\end{figure}

\begin{figure*}[!t]
        \centering
        \subfloat[Throughput]{\includegraphics[width=3.0in]{throughputs.png}}
        \hfil
        \subfloat[Network Usage]{\includegraphics[width=3.0in]{networkps.png}}
        \hfil
        \subfloat[Network Usage Bandwidth]{\includegraphics[width=3.0in]{networks.png}}
        \hfil
        \subfloat[CPU Load Average]{\includegraphics[width=3.0in]{loadaverages.png}}
        \caption{Scalability of the System}
        \label{scalability}
\end{figure*}

### 2014-10-18 paper/system_overview.tex
adding the paper in correct format

\begin{figure}
        \centering
        \includegraphics[width=0.6\textwidth]{processgraph.png}
        \caption{Process Graph}
        \label{processgraph}
\end{figure}

@@

\begin{figure}
        \centering
        \includegraphics[width=0.6\textwidth]{runtimegraph.png}
        \caption{Runtime Graph}
        \label{runtimegraph}
\end{figure}

@@

\lstinputlisting{interfaces.txt}

@@

\begin{figure}
        \centering
        \includegraphics[width=0.6\textwidth]{deployment.png}
        \caption{Deployment}
        \label{deployment}
\end{figure}

>>>>

\begin{figure}[!t]
	\centering
	\includegraphics[width=3.0in]{processgraph.png}
	\caption{Process Graph}
	\label{processgraph}
\end{figure}

@@

\begin{figure}[!t]
        \centering
        \includegraphics[width=3.0in]{runtimegraph.png}
        \caption{Runtime Graph}
        \label{runtimegraph}
\end{figure}

@@

\definecolor{dkgreen}{rgb}{0,0.6,0}
\definecolor{gray}{rgb}{0.5,0.5,0.5}
\definecolor{mauve}{rgb}{0.58,0,0.82}

\lstset{frame=tb,
  language=Java,
  aboveskip=3mm,
  belowskip=3mm,
  showstringspaces=false,
  columns=flexible,
  basicstyle={\small\ttfamily},
  numbers=none,
  numberstyle=\tiny\color{gray},
  keywordstyle=\color{blue},
  commentstyle=\color{dkgreen},
  stringstyle=\color{mauve},
  breaklines=true,
  breakatwhitespace=true,    
  tabsize=2
}

\begin{lstlisting}
public interface Event {
    public String getKey();
    public void serialize(DataOutput dataOutput);
    public void parse(DataInput dataInput);
}

public interface Element {
    public void initialise(Container container,
                     Map<String,String> parameters);
}

public interface Adaptor extends Element {
    public void start();
}

public interface Processor extends Element {
    public void onEvent(Event event);
}
\end{lstlisting}

@@

\begin{figure}[!t]
        \centering
        \includegraphics[width=3.0in]{deployment.png}
        \caption{Deployment}
        \label{deployment}
\end{figure}
